On the discretization of Laplace's equation with Neumann boundary conditions on polygonal domains

### 2020-01-21 paper_lap/JCP_submission/06num.tex
Adding jcp submission

\subsection{Performance}
In this section, we demonstrate the performance of the solver by solving a scattering problem in the
exterior of a ``broken wheel'' region. The boundary data is given by
\begin{equation}
f(x) = \nabla  \sum_{j=1}^{57} c_{j} \log| \bx - \bx_{j}| \cdot \bnu(\bx) \, , 
\end{equation}
where there is one $\bx_{j}$ located in each of the spokes, one of the $\bx_{j}$ is in the central disc, and the remaining $50$ $\bx_{j}$ are chosen randomly in the exrterior of the bounding disc containing the domain. The strengths $c_{j}$ are chosen such that they average to $0$. The domain contains $108$ corners, was discretized using $22240$ nodes and required $105$ iterations to converge to a residue of $10^{-15}$. The matrix at each iteration was applied using an FMM whose tolerance was also set to $10^{-15}$. The solution was computed in $15$ secs, and plotted at a $500\times 500$ grid of targets in $6.5$ secs. All of the results have been computed on a single core on a Macintosh machine with Intel core i5 2.3GHz processors. In~\cref{fig:magnetron}, we plot the scattered field, the boundary data, and the computed density.

>>>>

\subsection{Performance}
In this section, we demonstrate the performance of the solver by solving a scattering problem in the
exterior of a ``broken wheel'' region. The boundary data is given by
\begin{equation}
f(x) = \nabla  \sum_{j=1}^{57} c_{j} \log| \bx - \bx_{j}| \cdot \bnu(\bx) \, , 
\end{equation}
where there is one $\bx_{j}$ located in each of the spokes, one of the $\bx_{j}$ is in the central disc, and the remaining $50$ $\bx_{j}$ are chosen randomly in the exterior of the bounding disc containing the domain. The strengths $c_{j}$ are chosen such that they average to $0$. The domain contains $108$ corners, was discretized using $22240$ nodes and required $105$ iterations to converge to a residue of $10^{-15}$. The matrix at each iteration was applied using an FMM whose tolerance was also set to $10^{-15}$. The solution was computed in $15$ secs, and plotted at a $500\times 500$ grid of targets in $6.5$ secs. All of the results have been computed on a single core on a Macintosh machine with Intel core i5 2.3GHz processors. In~\cref{fig:magnetron}, we plot the scattered field, the boundary data, and the computed density.

### 2020-01-21 paper_lap/JCP_submission/manuscript.tex
Adding jcp submission

\documentclass[12pt]{article}
\usepackage{amsmath,amsthm,amssymb,amscd,fancybox,epsfig,float,subfigure}
\usepackage{authblk}
\usepackage[margin=1in]{geometry}
\usepackage{graphics}
\usepackage{epstopdf}
\usepackage{multirow}
\usepackage{hhline}
\usepackage{cleveref}
\usepackage{xcolor}
\usepackage{tikz}
\usetikzlibrary{arrows,automata}
\usepackage[nocompress]{cite}
\newtheorem{definition}{Definition}[section]
\newtheorem{remark}{Remark}[section]
\newtheorem{conjecture}{Conjecture}[section]
\newtheorem{proposition}{Proposition}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{remark1}{Remark}[section]
\newcommand{\beqn}{\begin{equation}}
\newcommand{\eeqn}{\end{equation}}
\newcommand{\psub}{\mbox{$\ddot{-}$}}
\newcommand{\cS}{\mathcal{S}}
\newcommand{\sgn}{{\rm sgn}}
\newcommand{\cN}{\mathcal{N}}
\newcommand{\cD}{\mathcal{D}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\bS}{\mathbb{S}}
\newcommand{\bR}{\mathbb{R}}
\newcommand{\cR}{\mathcal{R}}
\newcommand{\cI}{\mathcal{I}}
\newcommand{\cG}{\mathcal{G}}
\newcommand{\cH}{\mathcal{H}}
\newcommand{\cF}{\overline{\bf F}}
\newcommand{\cU}{\overline{\bf U}}
\newcommand{\cT}{\mathcal{T}}
\newcommand{\bP}{{\bf P}}
\newcommand{\bT}{\mathbb{T}}
\newcommand{\bq}{{\bf q}}
\newcommand{\bv}{{\bf v}}
\newcommand{\bu}{{\bf u}}
\newcommand{\boldf}{{\bf f}}
\newcommand{\bphi}{{\boldsymbol \phi}}
\newcommand{\bmu}{{\boldsymbol \mu}}
\newcommand{\brho}{{\boldsymbol \rho}}
\newcommand{\bC}{{\bf C}}
\newcommand{\bV}{{\bf V}}
\newcommand{\bU}{{\bf U}}
\newcommand{\bF}{{\bf F}}
\newcommand{\bRes}{{\bf R}}
\newcommand{\bM}{{\bf M}}
\newcommand{\bI}{\mathbb{I}}
\newcommand{\bN}{\mathbb{N}}
\newcommand{\bL}{\mathbb{L}}
\newcommand{\bX}{\mathbb{X}}
\newcommand{\bx}{\boldsymbol{x}}
\newcommand{\bnu}{\boldsymbol{\nu}}
\newcommand{\bn}{\boldsymbol{n}}
\newcommand{\by}{\boldsymbol{y}}
\newcommand{\cL}{\mathcal{L}}
\newcommand{\bub}{\underbar{b}}
\newcommand{\xmyo}{\sqrt{x^2 + y^2 - 2xy\cos{\pi \alpha}}}
\newcommand{\sina}{\sin{(\pi \alpha)}}
\newcommand{\sqsina}{\sin^{2}{(\pi \alpha)}}
\newcommand{\cosa}{\cos{(\pi \alpha)}}
\newcommand{\sinna}{\sin{(\pi \nu (1-\alpha))}}
\newcommand{\cosna}{\cos{(\pi \nu (1-\alpha))}}
\newcommand{\sinn}{\sin{(\pi \nu)}}
\newcommand{\cosn}{\cos{(\pi \nu)}}
\newcommand{\bbmat}{\begin{bmatrix}}
\newcommand{\ebmat}{\end{bmatrix}}
\newcommand{\dudn}[1]{\frac{\partial u_{#1}}{\partial n}}

@@

\begin{document}
 \title{On the discretization of Laplace's equation with Neumann boundary conditions on polygonal domains}
\author{Jeremy Hoskins\thanks{Applied Mathematics Program, Yale University, USA. \\ email: jeremy.hoskins@yale.edu}, \,
Manas Rachh\thanks{Center for Computational Mathematics, Flatiron Institute, USA. \\ email: mrachh@flatironinstitute.org}}
 \maketitle

@@

\section{Acknowledgements}
The authors would like to thank Leslie Greengard, and Vladimir Rokhlin for many useful discussions.

@@

With regards to the resolution of the of the function $\tilde{f}(s)$ on the given discretization of the boundary, 
we note that the closest singularity of the function $\tilde{f}(s)$ when restricted to a panel away from the corner
and not on the same edge as $\gamma([s_{1},s_{2}])$ is the closest point on the panel $\gamma([s_{1},s_{2}])$. 
However, by assumption 2, the error in resolving the function $\tilde{f}(s)$ using an $M$ point Gauss-Legendre
or Chebyshev panel is bounded by $C \rho_{0}^{-M}$. Note that the behavior of $\tilde{f}(s)$ in the complex plane is related
to the behavior of $k(s,t)$ in the complex $s$ plane and hence the constant $C$ is $O(1)$.
For the panels, at the corner, based on the proof in Appendix A, the error in resolving the function $\tilde{f}(s)$ when
truncated to a taylor series of order $N$ is less than $C 2^{-N}$, since all points on $\gamma([s_{1},s_{2}])$ are 
well-separated from corners by twice the panel length $r_{c}$. Thus, by making the panels small enough, $\rho$ can be increased arbitrarily to obtain desired tolerances on the boundary data $\tilde{f}(s)$ on the corresponding discretization of the boundary.

@@

 \bibliographystyle{plain}
 \bibliography{bib_file2}
\end{document}

>>>>

\documentclass[12pt]{elsarticle}
\usepackage{amsmath,amsthm,amssymb,amscd,fancybox,epsfig,float,subfigure}
\usepackage[margin=1in]{geometry}
\usepackage{graphics}
\usepackage{epstopdf}
\usepackage{multirow}
\usepackage{hhline}
\usepackage{cleveref}
\usepackage{xcolor}
\usepackage{tikz}
\usetikzlibrary{arrows,automata}
\newtheorem{definition}{Definition}[section]
\newtheorem{remark}{Remark}[section]
\newtheorem{conjecture}{Conjecture}[section]
\newtheorem{proposition}{Proposition}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{remark1}{Remark}[section]
\newcommand{\beqn}{\begin{equation}}
\newcommand{\eeqn}{\end{equation}}
\newcommand{\psub}{\mbox{$\ddot{-}$}}
\newcommand{\cS}{\mathcal{S}}
\newcommand{\sgn}{{\rm sgn}}
\newcommand{\cN}{\mathcal{N}}
\newcommand{\cD}{\mathcal{D}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\bS}{\mathbb{S}}
\newcommand{\bR}{\mathbb{R}}
\newcommand{\cR}{\mathcal{R}}
\newcommand{\cI}{\mathcal{I}}
\newcommand{\cG}{\mathcal{G}}
\newcommand{\cH}{\mathcal{H}}
\newcommand{\cF}{\overline{\bf F}}
\newcommand{\cU}{\overline{\bf U}}
\newcommand{\cT}{\mathcal{T}}
\newcommand{\bP}{{\bf P}}
\newcommand{\bT}{\mathbb{T}}
\newcommand{\bq}{{\bf q}}
\newcommand{\bv}{{\bf v}}
\newcommand{\bu}{{\bf u}}
\newcommand{\boldf}{{\bf f}}
\newcommand{\bphi}{{\boldsymbol \phi}}
\newcommand{\bmu}{{\boldsymbol \mu}}
\newcommand{\brho}{{\boldsymbol \rho}}
\newcommand{\bC}{{\bf C}}
\newcommand{\bV}{{\bf V}}
\newcommand{\bU}{{\bf U}}
\newcommand{\bF}{{\bf F}}
\newcommand{\bRes}{{\bf R}}
\newcommand{\bM}{{\bf M}}
\newcommand{\bI}{\mathbb{I}}
\newcommand{\bN}{\mathbb{N}}
\newcommand{\bL}{\mathbb{L}}
\newcommand{\bX}{\mathbb{X}}
\newcommand{\bx}{\boldsymbol{x}}
\newcommand{\bnu}{\boldsymbol{\nu}}
\newcommand{\bn}{\boldsymbol{n}}
\newcommand{\by}{\boldsymbol{y}}
\newcommand{\cL}{\mathcal{L}}
\newcommand{\bub}{\underbar{b}}
\newcommand{\xmyo}{\sqrt{x^2 + y^2 - 2xy\cos{\pi \alpha}}}
\newcommand{\sina}{\sin{(\pi \alpha)}}
\newcommand{\sqsina}{\sin^{2}{(\pi \alpha)}}
\newcommand{\cosa}{\cos{(\pi \alpha)}}
\newcommand{\sinna}{\sin{(\pi \nu (1-\alpha))}}
\newcommand{\cosna}{\cos{(\pi \nu (1-\alpha))}}
\newcommand{\sinn}{\sin{(\pi \nu)}}
\newcommand{\cosn}{\cos{(\pi \nu)}}
\newcommand{\bbmat}{\begin{bmatrix}}
\newcommand{\ebmat}{\end{bmatrix}}
\newcommand{\dudn}[1]{\frac{\partial u_{#1}}{\partial n}}

@@

\journal{Computational Physics}

\begin{document}

\begin{frontmatter}

 \title{On the discretization of Laplace's equation with Neumann boundary conditions on polygonal domains}
\author[jh]{Jeremy Hoskins}
\author[mr]{Manas Rachh}
\address[jh]{Applied Mathematics Program, Yale University, USA. \\ email: jeremy.hoskins@yale.edu}
\address[mr]{Center for Computational Mathematics, Flatiron Institute, USA. \\ email: mrachh@flatironinstitute.org}

\begin{abstract}
In the present paper we describe a class of algorithms for the solution of Laplace's equation on polygonal domains with Neumann boundary conditions. It is well known that in such cases the solutions have singularities near the corners which poses a challenge for many existing methods. 
If the boundary data is smooth on each edge of the polygon, then in the vicinity of each corner the solution to the corresponding boundary integral equation has an expansion in terms of certain (analytically available) singular powers. Using the known behavior of the solution, universal discretizations have been constructed for the solution of the Dirichlet problem. 
However, the leading order behavior of solutions to the Neumann problem is $O(t^{\mu})$ for $\mu \in (-1/2,0)$ depending on the angle at the corner (compared to $O(C+t^{\mu})$ with $\mu>1/2$ for the Dirichlet problem); this presents a significant challenge in the design of universal discretizations. Our approach is based on using the discretization for the Dirichlet problem in order to compute a solution in the ``weak sense'' by solving an adjoint linear system; namely, it can be used to compute inner products with smooth functions accurately, but it cannot be interpolated.  Furthermore we present a procedure to obtain accurate solutions arbitrarily close to the corner, by solving a sequence of small local subproblems in the vicinity of that corner. The results are illustrated with several numerical examples.
\end{abstract}

\begin{highlights}
\item Efficient discretization to boundary integral equations corresponding to Laplace's equation with Neumann boundary conditions based on an adjoint Dirichlet discretization resulting
in weak solutions to the integral equation. 
\item A local re-solve algorithm for obtaining pointwise accurate solutions of the integral equation arbitrarily close to the corner.
\item Rapid evaluation of solution at target locations in the volume arbitrarily close to the corner.
\end{highlights}

\begin{keyword}
Boundary value problems, Potential theory, Singular solutions, Integral equations, Corners
\end{keyword}

\end{frontmatter}

@@

\section{Acknowledgments}
J. Hoskins was supported in part by AFOSR FA9550-16-1-0175 and by the ONR (award no. N00014-14-1-0797).
The authors would like to thank Alex Barnett, Leslie Greengard, Michael O'Neil, and Vladimir Rokhlin for many useful discussions, and Jeremy Magland for providing sector plotting tools.

@@

With regards to the resolution of the of the function $\tilde{f}(s)$ on the given discretization of the boundary, 
we note that the closest singularity of the function $\tilde{f}(s)$ when restricted to a panel away from the corner
and not on the same edge as $\gamma([s_{1},s_{2}])$ is the closest point on the panel $\gamma([s_{1},s_{2}])$. 
However, by assumption 2, the error in resolving the function $\tilde{f}(s)$ using an $M$ point Gauss-Legendre
or Chebyshev panel is bounded by $C \rho_{0}^{-M}$. Note that the behavior of $\tilde{f}(s)$ in the complex plane is related
to the behavior of $k(s,t)$ in the complex $s$ plane and hence the constant $C$ is $O(1)$.
For the panels, at the corner, based on the proof in Appendix A, the error in resolving the function $\tilde{f}(s)$ when
truncated to a Taylor series of order $N$ is less than $C 2^{-N}$, since all points on $\gamma([s_{1},s_{2}])$ are 
well-separated from corners by twice the panel length $r_{c}$. Thus, by making the panels small enough, $\rho$ can be increased arbitrarily to obtain desired tolerances on the boundary data $\tilde{f}(s)$ on the corresponding discretization of the boundary.

@@

 \bibliographystyle{elsarticle-num}
 \bibliography{bib_file2}
\end{document}
